%-------------------------
% Resume in Latex
% Author : Gabriel Sison
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Random Stuff %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
% Sections formatting
\titleformat{\section}{
	\vspace{-7pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{0pt}]
% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Commands  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\resumeItem}[1]{
	\item\small{
		{#1 \vspace{-3pt}}
	}
}
\newcommand{\resumeSubheading}[4]{
	\vspace{-3pt}\item
	\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & \textbf{\small #2} \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubheadingContinue}[2]{
	\vspace{-3pt}
	\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
	\vspace{-3pt}\item
	\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & \textbf{\small #2} \\
	\end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{0pt}}
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Heading  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
	\begin{center}
		% NAME
		{\Huge\scshape Stefan Marcu} 
		% SUBHEADING
		\\ Senior Software Engineer\\
		\small
		% EMAIL
		\href{mailto:EMAIL}{\raisebox{-0.2\height}\faEnvelope\  \underline{stefan.ovidiu.marcu@gmail.com}} ~ 
		% LINKEDIN
		\href{LINK}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/stefan-ovidiu-marcu-57b462125}}  ~
		% MOBILE PHONE NUMBER
		\href{LINK}{\raisebox{-0.2\height}\faPhone\ \underline{07502099170}}
	\end{center}
	
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Experience  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Experience}
	\resumeSubHeadingListStart
	
	% COMPANY 1
	\resumeSubheading
	{Deliveroo}{London}
	% POSITION 1
	{POSITION 1}{December 2021 - December 2023}
	\resumeItemListStart
	\resumeItem{WHAT YOU DID}
	\resumeItem{WHAT YOU DID}
	\resumeItemListEnd
	
	% COMPANY 2
	\resumeSubheading
	{Zoopla}{London}
	% POSITION 1
	{Software Engineer}{January 2020 - December 2021}
	\resumeItemListStart
	\resumeItem{Architected, documented and built the new authentication system for Zoopla Pro using Auth0, with a live migration strategy.}
	\resumeItem{Built gRPC and REST services in Golang with Terraform-ed AWS infrastructure to manage property details, valuation reports, listings and user information. For all these services, monitoring and alerting was handled through Cloudwatch, Slack and NewRelic.}
	\resumeItem{Documented and built a new ingestion system in Golang for reporting data, handling 2-6 million requests/day.}
	\resumeItem{Set the standard in testing and project structure for multiple engineering teams interested in Golang.}
	\resumeItem{As part of the interviewing process, reviewed coding submissions in Golang, Java and Python. Observed customer interviews to better understand their needs and help shape new features.}
	\resumeItemListEnd
	
	% COMPANY 3
	\resumeSubheading
	{AND Digital}{London}
	% POSITION 0
	{Product Developer}{April 2018 - December 2019}

	% POSITION 1
	\resumeSubheadingContinue
	{Product Developer - IAG Cargo, British Airways}{}
	\resumeItemListStart
	\resumeItem{Finished the delivery of an MVP for an internal tool, written in Java, to keep track of specific types of parcels and to better manage the space available on planes (airmail). Upskilled one junior developer during the process by guiding and reviewing their Java back end work.}
	\resumeItemListEnd
	
	% POSITION 2
	\resumeSubheadingContinue
	{Product Developer - IAG Cargo, British Airways}{}
	\resumeItemListStart
	\resumeItem{Finished the delivery of an MVP for an internal tool, written in Java, to keep track of specific types of parcels and to better manage the space available on planes (airmail). Upskilled one junior developer during the process by guiding and reviewing their Java back end work.}
	\resumeItemListEnd
	
	% POSITION 3
	\resumeSubheadingContinue
	{Product Developer - PRS (Performing Right Society)}{}
	\resumeItemListStart
	\resumeItem{Discovery piece of work, collaborating with the CIO to research 5 products and understand the dependencies required. We provided PRS with an estimate of cost, time, team size and a better prioritised list of products to deliver.}
	\resumeItemListEnd
	
	% POSITION 4
	\resumeSubheadingContinue
	{AND Digital internal}{}
	\resumeItemListStart
	\resumeItem{Shadowed several interviews, prepared and reviewed candidates’ coding challenges. Mentored a few junior developers on different projects.}
	\resumeItem{Implemented a couple of internally used tools: an NLP component to provide information regarding client engagements, employees’ status updates and availability, as well as a dashboard handling the meeting rooms in the office and other regularly occurring internal events.}
	\resumeItemListEnd

	% COMPANY 4
	\resumeSubheading
	{Capital One}{London}
	% POSITION 1
	{Junior Software Engineer}{September 2017 - April 2018}
	\resumeItemListStart
	\resumeItem{Wrote a new internal service and several endpoints for existing Java micro services for new types of customers. Fixed various critical security issues including a live issue in production. Improved the test coverage of internal services by 28\%.}
	\resumeItem{Annotated the messages generated by the internal static analyser with relevant metadata, in order to reduce the time required to track the signaled issues.}
	\resumeItemListEnd
	
	% COMPANY 5
	\resumeSubheading
	{Capital One}{Nottingham}
	% POSITION 1
	{Intern Software Engineer}{July 2016 - September 2016}
	\resumeItemListStart
	\resumeItem{Built the initial version of an orchestration layer to make the development of internal APIs easier.}
	\resumeItemListEnd
	
	\resumeSubHeadingListEnd
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Education  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Education}
	\resumeSubHeadingListStart
	
	% MAIN INFORMATION
	\resumeSubheading
	{University of Oxford}{2014 - 2017}
	{BSC in Computer Science}{}
	
	\resumeSubHeadingListEnd
		
\end{document}
